A Survey on Ordered Binary Decision Diagrams

### 2015-09-10 paper.tex
Remove duplicate function definition
Add first two paragraphs to From BDDs to OBDDs section

Figure~\ref{fig:obdd} shows one possible ROBDD representation of
$f=(A \land B) \lor (B \land C)$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr

@@

>>>>

Figure~\ref{fig:obdd} shows one possible ROBDD representation of
$f$. The following section covers the details of how
to derive the OBDD representation from a BDD. \tbr

@@

As the name suggests, \textit{Reduced} Ordered Binary Decision Diagrams are a 
minimized representation of BDDs. Furthermore, the decision variables are ordered
consistently. More formally, for any node $\upsilon$ and their respective children
$\omega_1$ and $\omega_2$, a total ordering is imposed, i.e.
$var(\upsilon) < var(\omega_1)$ and $var(\upsilon) < var(\omega_2)$, respectively,
where $var(x)$ denotes the label of node $x$.

This \textit{variable ordering} affects the efficiency of the symbolic
manipulation because different variable orderings, in general, produce different
OBDDs. In the worst case, this will result in exponential complexity for bad
orderings. Nevertheless, as will be described in Section~\ref{sec:limitations},
there exist classes of functions for which the OBDD complexity is exponential
regardless of which variable ordering is chosen.

\tbr
